\pkg{cv}: An \proglang{R} Package for Cross-Validation of Regression Models

### 2024-01-04 scratch/notes_john/JSS-article/JSS-article-reduced.Rmd
try multicolumn figure

---
documentclass: jss
author:
  - name: John Fox
    orcid: 0000-0002-1196-8012
    affiliation: 'McMaster University'
    address: |
      | Hamilton, Ontario, Canada
    email: \email{jfox@mcmaster.ca}
    url: https://www.john-fox.ca/
  - name: Georges Monette
    orcid: 0000-0000-0000-0000
    affiliation: 'York University'
    # To add another line, use \AND at the end of the previous one as above
    address: |
      | Toronto, Ontario, Canada
title:
  formatted: "\\pkg{cv}: An \\proglang{R} Package for Cross-Validation of Regression Models"
  # If you use tex in the formatted title, also supply version without
  plain:     "cv: An R Package for Cross-Validation of Regression Models"
  # For running headers, if needed
  short:     "\\pkg{cv}: Cross-Validation"
abstract: >
  The abstract of the article.
keywords:
  # at least one keyword must be supplied
  formatted: [cross-validation, regression analysis, model selection, "\\proglang{R}"]
  plain:     [cross-validation, regression analysis, model selection, R]
preamble: >
  \usepackage{amsmath}
output: rticles::jss_article
bibliography: ["cv.bib"]
---

@@

```{r, polynomial-regression-CV-graph-2, fig.show="hold"}
#| out.width = "45%",
#| fig.height = 6,
#| fig.cap = "Cross-validated 10-fold and LOO MSE as a function of polynomial degree, $p$"
plot(cv.auto.10, main="Polynomial Regressions, 10-Fold CV",
     axis.args=list(labels=1:10), xlab="Degree of Polynomial, p")
plot(cv.auto.loo, main="Polynomial Regressions, LOO CV",
     axis.args=list(labels=1:10), xlab="Degree of Polynomial, p")
```

>>>>

---
documentclass: jss
author:
  - name: John Fox
    orcid: 0000-0002-1196-8012
    affiliation: 'McMaster University'
    address: |
      | Hamilton, Ontario, Canada
    email: \email{jfox@mcmaster.ca}
    url: https://www.john-fox.ca/
  - name: Georges Monette
    orcid: 0000-0000-0000-0000
    affiliation: 'York University'
    # To add another line, use \AND at the end of the previous one as above
    address: |
      | Toronto, Ontario, Canada
title:
  formatted: "\\pkg{cv}: An \\proglang{R} Package for Cross-Validation of Regression Models"
  # If you use tex in the formatted title, also supply version without
  plain:     "cv: An R Package for Cross-Validation of Regression Models"
  # For running headers, if needed
  short:     "\\pkg{cv}: Cross-Validation"
abstract: >
  The abstract of the article.
keywords:
  # at least one keyword must be supplied
  formatted: [cross-validation, regression analysis, model selection, "\\proglang{R}"]
  plain:     [cross-validation, regression analysis, model selection, R]
preamble: >
  \usepackage{amsmath}
output: 
  rticles::jss_article:
    extra_dependencies: "subfig"
bibliography: ["cv.bib"]
---

@@

```{r, polynomial-regression-CV-graph-2, fig.show="hold"}
#| fig.height = 5,
#| fig.cap = "Cross-validated (a) 10-fold and (b) LOO MSE as a function of polynomial degree, $p$",
#| fig.subcap=c('', ''),
#| fig.ncol = 2, out.width = "50%", fig.align = "center"
plot(cv.auto.10, main="Polynomial Regressions, 10-Fold CV",
     axis.args=list(labels=1:10), xlab="Degree of Polynomial, p")
plot(cv.auto.loo, main="Polynomial Regressions, LOO CV",
     axis.args=list(labels=1:10), xlab="Degree of Polynomial, p")
```

### 2024-01-04 scratch/notes_john/JSS-article/JSS-article-reduced.tex
try multicolumn figure

@@

Residual standard error: 4.374 on 389 degrees of freedom
Multiple R-squared:  0.6876,    Adjusted R-squared:  0.686 
F-statistic:   428 on 2 and 389 DF,  p-value: < 2.2e-16
\end{CodeOutput}
\begin{CodeInput}
R> cv(m.auto)
\end{CodeInput}
\begin{CodeOutput}
R RNG seed set to 423836
\end{CodeOutput}
\begin{CodeOutput}
10-Fold Cross Validation
method: Woodbury
criterion: mse
cross-validation criterion = 19.26863
bias-adjusted cross-validation criterion = 19.25351
full-sample criterion = 18.98477 
\end{CodeOutput}
\end{CodeChunk}

@@

{\centering \includegraphics[width=0.45\linewidth]{JSS-article-reduced_files/figure-latex/polynomial-regression-CV-graph-2-1} \includegraphics[width=0.45\linewidth]{JSS-article-reduced_files/figure-latex/polynomial-regression-CV-graph-2-2}

@@

\caption[Cross-validated 10-fold and LOO MSE as a function of polynomial degree, $p$]{Cross-validated 10-fold and LOO MSE as a function of polynomial degree, $p$}\label{fig:polynomial-regression-CV-graph-2}
\end{figure}
\end{CodeChunk}

>>>>

\usepackage{subfig}

@@

Residual standard error: 4.374 on 389 degrees of freedom
Multiple R-squared:  0.6876,    Adjusted R-squared:  0.686 
F-statistic:   428 on 2 and 389 DF,  p-value: < 2.2e-16
\end{CodeOutput}
\begin{CodeInput}
R> cv(m.auto)
\end{CodeInput}
\begin{CodeOutput}
R RNG seed set to 886597
\end{CodeOutput}
\begin{CodeOutput}
10-Fold Cross Validation
method: Woodbury
criterion: mse
cross-validation criterion = 19.41669
bias-adjusted cross-validation criterion = 19.39385
full-sample criterion = 18.98477 
\end{CodeOutput}
\end{CodeChunk}

@@

{\centering \subfloat[\label{fig:polynomial-regression-CV-graph-2-1}]{\includegraphics[width=0.5\linewidth]{JSS-article-reduced_files/figure-latex/polynomial-regression-CV-graph-2-1} }\subfloat[\label{fig:polynomial-regression-CV-graph-2-2}]{\includegraphics[width=0.5\linewidth]{JSS-article-reduced_files/figure-latex/polynomial-regression-CV-graph-2-2} }

@@

\caption[Cross-validated (a) 10-fold and (b) LOO MSE as a function of polynomial degree, $p$]{Cross-validated (a) 10-fold and (b) LOO MSE as a function of polynomial degree, $p$}\label{fig:polynomial-regression-CV-graph-2}
\end{figure}
\end{CodeChunk}
